---
title: "Assignment 10"
author: "Nimish Sakalle"
date: "NOvember 19, 2016"
output:
  html_document:
    keep_md: yes
  pdf_document: default
  word_document: default
subtitle: Analysis.
---
  
```{r}
## The first step is to load R libraries that are required for the analysis.

library(plyr)
library(ggplot2)
library(knitr)
```
###**Making environment ready**
```{r setup, include=FALSE}
knitr::opts_chunk$set(root.dir = "~/RProject/Assignment10")
knitr::opts_chunk$set(echo = FALSE)
```

###** Reading from file into data frame **

```{r}
# Setting working directory
setwd("C:\\RProject\\Assignment 10")

# Reading file into GDP data frame
ny1raw <- read.csv("nyt1.csv", header=TRUE)

#keeping backup of original file for future
ny1backup <- ny1raw

# Checking for file header names.
names(ny1raw)

# Files header and first few attributes.
head(ny1raw)

# This commands give information about attributes data type.
str(ny1raw)

# This is to get the number of rows in file.
NROW(ny1raw)
```

###** Creating data grouping into variable AgeGroup **
```{r}
ny1raw$Agegroup <- cut(ny1raw$Age, c(-Inf,18,24,34,44,54,64,Inf))
ny1raw$Agegroup = factor(ny1raw$Agegroup,labels=c("<18","18-24","25-34","35-44","45-54","55-64","65+"))
head(ny1raw)
```
###** CReating subset for Impression >0 **
```{r}
Impsub <- subset(ny1raw, Impressions>0)
head(Impsub)
```
###** New variable Click Through Rate **
```{r}
Impsub$CTR <- Impsub$Clicks/Impsub$Impressions
head(Impsub)
```
###** Analysis of Click Stream  **
###** gPlot distributions of number impressions and click-through-rate (CTR = click/impression) for the age groups**
```{r}
ggplot(subset(Impsub, CTR>0), aes(x=CTR, fill=Agegroup))+labs(title='Click through rate by Age Group')+ geom_histogram(binwidth = .020)

```
###** new variable CTR Behavior**
```{r}
Impsub$CTR <- cut(Impsub$CTR, c(-Inf, .2,.4,.6,.8, Inf))
Impsub$CTR <- factor(Impsub$CTR, labels=c("<.2",".2-.4",".4-.6",".6-.8",">.8"))
head(Impsub)
```
###**Subset for male and Female and sum of Impression, CLicks and Signed_In**
```{r}
ImpsubMale <- subset(Impsub,Gender==1)
# Total number of Male
nrow(ImpsubMale)
ImpsubFemale <- subset(Impsub,Gender==0)

# Total number of Female
nrow(ImpsubFemale)

# Total Number of Impression
sum(Impsub$Impressions)

# Total Number of Clicks
sum(Impsub$Clicks)

# Total Number of Clicks
sum(Impsub$Signed_In)

```
###**Mean of Age, Impressions, CLicks, and percentage of males and Signed_In**
```{r}
# Mean of Age
mean(Impsub$Age)
#Mean of Clicks
mean(Impsub$Clicks)
#Mean of Impressions
mean(Impsub$Impressions)
#Mean of Signed In
mean(Impsub$Signed_In)
```
###**Mean of Age, Impressions, CLicks, and percentage of males and Signed_In by Age Group**
```{r}
# Mean of Age by agegroup
aggregate(Impsub[,1], list(Impsub$Agegroup), mean)

# Mean of Clicks by agegroup
aggregate(Impsub[,4], list(Impsub$Agegroup), mean)

# Mean of Impression by agegroup
aggregate(Impsub[,3], list(Impsub$Agegroup), mean)

# Mean of Signed_In by agegroup
aggregate(Impsub[,5], list(Impsub$Agegroup), mean)
```

###** Create a table of CTRGroup vs AgeGroup counts **
```{r}
table(Impsub$CTR,Impsub$Agegroup)
```
##** Histogram of Clicks by ageGroup **
```{r}
ggplot(Impsub, aes(x=Clicks, fill=Agegroup))+geom_histogram(binwidth = 1)
```
###EOF###
